MyTitle

### 2024-11-01 paper/main.tex
updated

\usepackage{graphicx} 
\usepackage{luacode}  
\usepackage{ascmac}
\usepackage{comment}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{newtxtext, newtxmath}

@@

% Isabelle --------------------------------------------------------------------------------------------
\usepackage{listings}
\definecolor{isarblue}{HTML}{006699}
\definecolor{isargreen}{HTML}{009966}
\lstdefinelanguage{isabelle}{%
    keywords=[1]{type_synonym,datatype,fun,abbreviation,definition,proof,lemma,theorem,corollary},
    keywordstyle=[1]\bfseries\color{isarblue},
    keywords=[2]{where,assumes,shows,and,theorem,lemma},
    keywordstyle=[2]\bfseries\color{isargreen},
    keywords=[3]{if,then,else,case,of,SOME,let,in,O},
    keywordstyle=[3]\color{isarblue},
}
\lstset{%
  language=isabelle,
  escapeinside={&}{&},
  columns=fixed,
  extendedchars,
  basewidth={0.5em,0.45em},
  basicstyle=\ttfamily,
  mathescape,
}

@@

\def\isadelimtheory{}\def\endisadelimtheory{}
\def\isatagtheory{}\def\endisatagtheory{}
\def\isadelimML{}\def\endisadelimML{}
\def\isadelimdocument{}\def\endisadelimdocument{}
\def\isatagML{}\def\endisatagML{}
\def\isatagdocument{}\def\endisatagdocument{}
\def\isafoldML{}
\def\isadelimproof{}\def\endisadelimproof{}
\def\isatagproof{}\def\endisatagproof{}
\def\isafoldproof{}

\usepackage{isabelle,isabellesym}
\isabellestyle{it} % optional
\newcommand{\SNIPTEXT}[1]{#1} % remove #1 to ignore text commands
\newcommand{\SNIP}[2]{\expandafter\newcommand\csname snippet--#1\endcsname{#2}}

@@

% \SnippetPart{n}{m}{name}: the snippet `name' from line `n' to line `m' inclusive
\newcommand{\SnippetPart}[3]{{%
  \newcount\i
  \i=#1
  \loop
    \ifnum \i=#2
      \renewcommand{\isanewline}{}%
    \fi
    \GetSnip{#3-\the\i}%
    \advance \i 1
    \ifnum \i>#2 {}
    \else \repeat
}}
% -----------------------------------------------------------------------------------------------------

@@

\section{Defining Symmetric Extensions}
First, we define symmetric extensions in Isabelle/ZF.
We define automorphisms on $\Pbb$, the group of automorphisms $\Gcal$, and the normal filter $\Fcal$.
Basically, we work within the locale.

\begin{lstlisting}
  theory ZF_notAC_main_theorem : "x = y" 
  proof - 
    have "x = y" sorry
  qed 
\end{lstlisting}

\begin{isabelle}
\Snippet{ZF-notAC:theorem:ZF-notAC-main-theorem}
\end{isabelle}

>>>>

\usepackage{graphicx} 
\usepackage{luacode}  
\usepackage{ascmac}
\usepackage{comment}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{newtxtext,newtxmath}

\usepackage{fontspec}
\setmonofont{NOTOSANSMATH-REGULAR.TTF}

@@

% Isabelle --------------------------------------------------------------------------------------------

\usepackage[outputdir=out]{minted}

@@

\def\isadelimtheory{}\def\endisadelimtheory{}
\def\isatagtheory{}\def\endisatagtheory{}
\def\isadelimML{}\def\endisadelimML{}
\def\isadelimdocument{}\def\endisadelimdocument{}
\def\isatagML{}\def\endisatagML{}
\def\isatagdocument{}\def\endisatagdocument{}
\def\isafoldML{}
\def\isadelimproof{}\def\endisadelimproof{}
\def\isatagproof{}\def\endisatagproof{}
\def\isafoldproof{}
\usepackage{isabelle,isabellesym}
\isabellestyle{it} % optional
\newcommand{\SNIPTEXT}[1]{#1} % remove #1 to ignore text commands
\newcommand{\SNIP}[2]{\expandafter\newcommand\csname snippet--#1\endcsname{#2}}

@@

% \SnippetPart{n}{m}{name}: the snippet `name' from line `n' to line `m' inclusive
\newcommand{\SnippetPart}[3]{{%
  \newcount\i
  \i=#1
  \loop
    \ifnum \i=#2
      \renewcommand{\isanewline}{}%
    \fi
    \GetSnip{#3-\the\i}%
    \advance \i 1
    \ifnum \i>#2 {}
    \else \repeat
}}
% -----------------------------------------------------------------------------------------------------
\usepackage{listingsutf8}
\definecolor{isarblue}{HTML}{006699}
\definecolor{isargreen}{HTML}{009966}
\lstdefinelanguage{isabelle}{%
    keywords=[1]{type_synonym,datatype,fun,abbreviation,definition,proof,lemma,theorem,corollary},
    keywordstyle=[1]\bfseries\color{isarblue},
    keywords=[2]{where,assumes,shows,and,theorem,lemma},
    keywordstyle=[2]\bfseries\color{isargreen},
    keywords=[3]{if,then,else,case,of,SOME,let,in,O},
    keywordstyle=[3]\color{isarblue},
}
\lstset{%
  language=isabelle,
  escapeinside={&}{&},
  columns=fixed,
  extendedchars,
  basewidth={0.5em,0.45em},
  basicstyle=\ttfamily,
  mathescape,
  inputencoding=utf8
}

@@

\section{Defining Symmetric Extensions}
First, we define symmetric extensions in Isabelle/ZF.
We define automorphisms on $\Pbb$, the group of automorphisms $\Gcal$, and the normal filter $\Fcal$.
Basically, we work within the locale ∈.

\lstset{inputencoding=utf8/utf8}
\lstinputlisting[language=C++]{aaaa.thy}

\begin{lstlisting}
  theory ZF_notAC_main_theorem : "x = y" 
  proof - 
    have "x = y" sorry
  qed

lemma P_name_induct : 
"∀x ∈ P_names. (∀y. ∀ p. <y, p> ∈ x ⟶ Q(y)) ⟶ Q(x) ⟹ x ∈ P_names ⟹ Q(x)"
proof (rule_tac P_rank_induct, clarify)
\end{lstlisting}
\begin{minted}[linenos]{isabelle}

  theory ZF_notAC_main_theorem : "x ∈ y"
  proof - 
    have "x ∈ y" sorry
  qed
      \end{minted}

\begin{isabelle}
  \texttt{
\Snippet{ZF-notAC:theorem:ZF-notAC-main-theorem}
  }
\end{isabelle}
